Happiness in America: A Comprehensive Analysis of the Effects of Demographic Factors

### 2023-03-16 outputs/paper/Happiness in America: A Comprehensive Analysis of the Effects of Demographic Factors.qmd
title, author changed for final paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Happiness in America: A Comprehensive Analysis of the Effects of Demographic Factors"
author: 
  - Rae Zhang
  - Faustine Fan
  - Myra Li
thanks: "Code and data are available at: https://github.com/JunweiZhang130/Happiness-in-America-A-Comprehensive-Analysis-of-the-Effects-of-Demographic-Factors.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib

---
